Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-03-13 Master Thesis/synopsis.tex
Add items to bibliography

\begin{proof}
See Valued Fields 3.4.1 and 3.4.3.
\end{proof}

@@

\begin{proof}
See [ZS] VI §17 Theorem 38, §17 Theorem 40.
\end{proof}

@@

\begin{proof}
See Valued Fields 2.3, 4.1.4, [ZS] VI §3 Theorem 3.
\end{proof}

@@

\begin{proof}
See Valued Fields Lemma 5.2.1, Lemma 5.2.2, Theorem 5.2.5.
\end{proof}

@@

\begin{proof}
See Valued Fields 5.2.7.
\end{proof}

@@

\begin{proof}
Let $\overline{w}$ be the extension of $w\in\operatorname{Spv}(K_w)$ on $K^\text{s}$. By Valued Fields 3.1.5 we can find an extension $\overline{v}$ of $v$ on $K^\text{s}$ such that $\overline{w}$ is a specialization of $\overline{v}$. Let $K_v$ be the fixed field of $G_{\overline{v}}\subset G_K$.

Let $\sigma\in G_{\overline{w}}$. Then both $\mathcal{O}_{\overline{v}}$ and $\sigma(\mathcal{O}_{\overline{v}})$ are overrings of $\mathcal{O}_{\overline{w}}$. Now the overrings of valuation rings are totally ordered by inclusion and correspond to localizations of $\mathcal{O}_{\overline{w}}$ at prime ideals (See Valued Fields 2.3). Since $\mathcal{O}_{\overline{v}}$ and $\sigma(\mathcal{O}_{\overline{v}})$ have the same Krull dimension, they must be the same, thus $\sigma\in G_{\overline{v}}$. This proves $K_v\subset K_w$.

@@

\begin{proof}
See Valued Fields 4.4.1.
\end{proof}

@@

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension ([ZS], Ch. VI, §11, Lemma 2).
\end{proof}

@@

\begin{proof}
See [ZS] VI §10 Theorem 18
\end{proof}

>>>>

\begin{proof}
See \cite{EP05} 3.4.1 and 3.4.3.
\end{proof}

@@

\begin{proof}
See \cite{ZS60} VI §17 Theorem 38, §17 Theorem 40.
\end{proof}

@@

\begin{proof}
See \cite{EP05} 2.3, 4.1.4, \cite{ZS60} VI §3 Theorem 3.
\end{proof}

@@

\begin{proof}
See \cite{EP05} Lemma 5.2.1, Lemma 5.2.2, Theorem 5.2.5.
\end{proof}

@@

\begin{proof}
See \cite{EP05} 5.2.7.
\end{proof}

@@

\begin{proof}
Let $\overline{w}$ be the extension of $w\in\operatorname{Spv}(K_w)$ on $K^\text{s}$. By \cite{EP05} 3.1.5 we can find an extension $\overline{v}$ of $v$ on $K^\text{s}$ such that $\overline{w}$ is a specialization of $\overline{v}$. Let $K_v$ be the fixed field of $G_{\overline{v}}\subset G_K$.

Let $\sigma\in G_{\overline{w}}$. Then both $\mathcal{O}_{\overline{v}}$ and $\sigma(\mathcal{O}_{\overline{v}})$ are overrings of $\mathcal{O}_{\overline{w}}$. Now the overrings of valuation rings are totally ordered by inclusion and correspond to localizations of $\mathcal{O}_{\overline{w}}$ at prime ideals (See \cite{EP05} 2.3). Since $\mathcal{O}_{\overline{v}}$ and $\sigma(\mathcal{O}_{\overline{v}})$ have the same Krull dimension, they must be the same, thus $\sigma\in G_{\overline{v}}$. This proves $K_v\subset K_w$.

@@

\begin{proof}
See \cite{EP05} 4.4.1.
\end{proof}

@@

The second assertion follows from the first one, applied to $L$, by using the following equation of supernatural numbers ([E], Theorem 20.21):
\[ [L:K] = (\Gamma':\Gamma) \cdot [k':k]\cdot p^d \]
for some $d \leq \infty$, where $\Gamma'$ denotes the value group and $k'$ the residue field of the unique prolongation of $w$ to $L$. Note that $\operatorname{rank}(w) = \operatorname{rank}(v)$ in an algebraic field extension (\cite{ZS60}, Ch. VI, §11, Lemma 2).
\end{proof}

@@

\begin{proof}
See \cite{ZS60} VI §10 Theorem 18
\end{proof}
